|

### 2021-07-06 article/customerDropoutMembership.Rmd
upd

---
title: |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. The current template adapts part of the Rmd code by [Paul C. Bauer](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown), Mannheim Centre for European Social Research.]\vspace{0.5cm}
  |
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
---

```{r Setup, include=FALSE}
   knitr::opts_chunk$set(cache = FALSE)
   # Use chache = TRUE if you want to speed up compilation
   # set path
   # get rmarkdown directory
   caminho<-getwd()
   # set working directory
   setwd(caminho)
   print(caminho)

   # A function to allow for showing some of the inline code
   rinline <- function(code){
     html <- '<code  class="r">``` `r CODE` ```</code>'
     sub("CODE", code, html)

@@

   ##knitr::opts_chunk$set(python.reticulate=FALSE)

@@

```{r RETICULATE,echo=FALSE}
#Sys.setenv(RETICULATE_PYTHON = "C:/Program Files/Python39/python.exe")
#library(reticulate)
#use_virtualenv("C:/Users/mangelo.EEG/Documents/python")
```

@@

Context:
An organization membership located in portugal. The organization offers an annual membership
for the members, the service subscription has several payment options:

@@

```{r Stats, echo=TRUE, message=FALSE}
library(dplyr)
library(dlookr)
library(ggplot2)

##eda_report(nlswork,output_dir = "C:/Users/mangelo.EEG/Documents/GitHub/prjs/reports/",output_file = "eda_report.pdf")

@@

names(airquality)
##summary(nlswork)

## Missing values

library(visdat)
vis_dat(airquality)

@@

The average age in our data is `r round(mean(airquality$Temp,na.rm=TRUE),1)`.

@@

```{r Export Stats, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
stargazer(cars,
          title = "Summary table with stargazer",
          label="tab1cars",
          table.placement = "h",
          header=FALSE)
```

@@

```{r Export Regressions, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
model1 <- lm(speed ~ dist, data = cars)
model2 <- lm(speed ~ dist, data = cars)
model3 <- lm(dist ~ speed, data = cars)
stargazer(model1, model2, model3,
          title = "Regression table with stargazer",
          label="tab2",
          table.placement = "h",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE)
```

@@

```{r Figures 1, fig-1, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="h", message=FALSE, warning=FALSE, paged.print=FALSE}
plot(cars$speed, cars$dist)
```

@@

```{r Fig-2, fig.align="center", fig.cap="Miles per gallon according to the weight", fig.pos="h", fig.width=6, fig.height=3, message=FALSE, warning=FALSE, paged.print=FALSE}
mtcars$cyl <- as.factor(mtcars$cyl) # Convert cyl to factor
library(ggplot2)
ggplot(mtcars, aes(x=wt, y=mpg, shape=cyl)) + geom_point() +
  labs(x="Weight (lb/1000)", y = "Miles/(US) gallon",
       shape="Number of \n Cylinders") + theme_classic()
```

## Another example using Plotly
With `Plotly` we can produce interactive graphs which play well, for example, once can embeded in html webpages (drop by  [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/) for an example). One can insert this type of graphs in R Markdown PDF using `Orca` (it generates static images from Plotly graphs). Go [here](https://github.com/plotly/orca#installation) to check how to install it. See Figure \@ref(fig:fig-3) for an example.

```{r Fig-3, message=FALSE, warning=FALSE}
library(plotly)
p <- plot_ly(cars, type = "scatter", mode="markers",
        x=~speed,
        y=~dist)
#Sys.setenv('MAPBOX_TOKEN' = '12423423') # set arbitrary token
#orca(p, "logs/plotly-plot.pdf")
```

\begin{figure}[ht]
\centering
\caption{Example: export a Plotly figure using `orca`}\label{fig:fig-3}
		\includegraphics[width=0.9\linewidth]{../figures/teste.png}
\begin{flushleft}
\end{flushleft}
\end{figure}
\vspace{-1.2cm}

@@

\begin{equation}
f\left(k\right)=\binom{n}{k}p^k\left(1-p\right)^{n-k} \label{eq:binom}
\end{equation}

@@

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
stargazer(cars,
          title = "Summary 24",
          label="tab24",
          table.placement = "ht",
          header=FALSE)
```

@@

<div id="refs"></div>

@@

```{r fig-versioning, echo=TRUE}
cat(paste("#", capture.output(sessionInfo()), "\n", collapse =""))
  # or use message() instead of cat()
```

>>>>

---
title: |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. The current template adapts part of the Rmd code by [Paul C. Bauer](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown), Mannheim Centre for European Social Research.]\vspace{0.5cm}
  |
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
---

```{r Setup, include = FALSE}
   knitr::opts_chunk$set(cache = FALSE)
   # Use cache = TRUE if you want to speed up compilation
   # set path
   # get rmarkdown directory
   caminho <- getwd()
   # set working directory
   setwd(caminho)
   print(caminho)

   # A function to allow for showing some of the inline code
   rinline <- function(code) {
     html <- '<code  class = "r">``` `r CODE` ```</code>'
     sub("CODE", code, html)

@@

   ##knitr::opts_chunk$set(python.reticulate = FALSE)

@@

```{r RETICULATE,echo = FALSE}
#Sys.setenv(RETICULATE_PYTHON = "C:/Program Files/Python39/python.exe")
#library(reticulate)
#use_virtualenv("C:/Users/mangelo.EEG/Documents/python")
```

@@

Context:
An organization membership located in Portugal. The organization offers an annual membership
for the members, the service subscription has several payment options:

@@

```{r Stats, echo = TRUE, message = FALSE}
library(dplyr)
library(dlookr)
library(ggplot2)

#eda_report(nlswork,output_dir  = 
#	"C:/Users/mangelo.EEG/Documents/GitHub/prjs/reports/",
#	output_file = "eda_report.pdf")

@@

names(airquality)
#summary(nlswork)

## Missing values
library(visdat)
vis_dat(airquality)

@@

The average age in our data is `r round(mean(airquality$Temp,na.rm = TRUE),1)`.

@@

```{r Export Stats, echo = TRUE, message = FALSE, warning = FALSE, paged.print = FALSE, results = "asis"}
library(stargazer)
stargazer(cars,
          title = "Summary table with stargazer",
          label = "tab1cars",
          table.placement = "h",
          header = FALSE)
```

@@

```{r Export Regressions, echo = TRUE, message = FALSE, warning = FALSE, paged.print = FALSE, results = "asis"}
library(stargazer)
model1 <- lm(speed ~ dist, data = cars)
model2 <- lm(speed ~ dist, data = cars)
model3 <- lm(dist ~ speed, data = cars)
stargazer(model1, model2, model3,
          title = "Regression table with stargazer",
          label = "tab2",
          table.placement = "h",
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header = FALSE)
```

@@

```{r Figures 1, fig-1, fig.align = "center", fig.cap = "Scatterplot of Speed and Distance", fig.pos = "h", message = FALSE, warning = FALSE, paged.print = FALSE}
plot(cars$speed, cars$dist)
```

@@

```{r Fig-2, fig.align = "center", fig.cap = "Miles per gallon according to the weight", fig.pos = "h", fig.width = 6, fig.height = 3, message = FALSE, warning = FALSE, paged.print = FALSE}
mtcars$cyl <- as.factor(mtcars$cyl) # Convert cyl to factor
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg, shape = cyl)) + geom_point() +
  labs(x = "Weight (lb/1000)", y = "Miles/(US) gallon",
       shape = "Number of \n Cylinders") + theme_classic()
```

## Another example using Plotly
With `Plotly` we can produce interactive graphs which play well, for example, once can embedded 
in html webpages (drop by  [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/) 
for an example). One can insert this type of graphs in R Markdown PDF using `Orca` (it generates 
static images from Plotly graphs). 
Go [here](https://github.com/plotly/orca#installation) to check how to install it. 
See Figure \@ref(fig:fig-3) for an example.

```{r Fig-3, message = FALSE, warning = FALSE}
library(plotly)
p <- plot_ly(cars, type = "scatter", mode = "markers",
        x = ~speed,
        y = ~dist)
#Sys.setenv('MAPBOX_TOKEN' = '12423423') # set arbitrary token
#orca(p, "logs/plotly-plot.pdf")
```

\begin{figure}[ht]
\centering
\caption{Example: export a Plotly figure using `orca`}\label{fig:fig-3}
	\includegraphics[width = 0.9\linewidth]{../figures/teste.png}
\begin{flushleft}
\end{flushleft}
\end{figure}
\vspace{-1.2cm}

@@

\begin{equation}
f\left(k\right) = \binom{n}{k}p^k\left(1-p\right)^{n-k} \label{eq:binom}
\end{equation}

@@

```{r echo = TRUE, message = FALSE, warning = FALSE, paged.print = FALSE, results = "asis"}
library(stargazer)
stargazer(cars,
          title = "Summary 24",
          label = "tab24",
          table.placement = "ht",
          header = FALSE)
```

@@

<div id = "refs"></div>

@@

```{r fig-versioning, echo = TRUE}
cat(paste("#", capture.output(sessionInfo()), "\n", collapse  = ""))
  # or use message() instead of cat()
```
